---
title: "Complex in-built objects in R"
author: "Luciano Gabbanelli"
date: "2022-10-10"
output:
  html_document:
    toc: true
    toc_float: true
    collapse: true
    smooth_scroll: true
    theme: journal
    highlight: kate
    df_print: paged
    code_folding: show
---
# Control Flow Structures:


## 1. Greter than 10

```{r}
a <- sample(20,1)
a
if (a > 10) {
  
  if (a %% 2 == 0) {
    TRUE
  } else {
    FALSE
  }
  
} else {
  
  print(a/2)
  
}
```



## 2. Squares of maximum and minumum

```{r}

my.vec <- round(runif(25,1,50)); my.vec

if (max(my.vec) > (2*min(my.vec))) {
  print(min(my.vec)^2)
} else if (max(my.vec) < (2*min(my.vec))){
  print(max(my.vec)^2)
} else {
    print(sort(my.vec, decreasing=TRUE))
  }

```



## 3. Multiples of 3 and/or 5:

```{r}
for (n in 1:100) {
  if (n %% 3 == 0 & n %% 5 == 0) {print(paste(n,"is multiple of both, 3 and 5."))}
  else if (n %% 3 == 0) {print(paste(n,"is multiple of 3."))}
  else if (n %% 5 == 0) {print(paste(n,"is multiple of 5."))}
}
```



## 4. Scary math

```{r}
my.sum = 0
my.prod = 1
for (n in 0:4){
  my.sum <- my.sum + 3*n
  if (n == 0){
    next
  } else{
    my.prod <- my.prod*2*n
  }
}

cat(my.sum, my.prod)
```



## 5. Random < 1

```{r}

repeat {
  x <- rnorm(1)
  print(x)
  
  if (x > 1){
    break
  }
}

while (TRUE) {
  x <- rnorm(1)
  print(x)
  if (x > 1) {
    break
  }
}
```



## 6. Salary

```{r}

salary <- as.numeric(readline("Introduce a salary: "))

if (salary > 1750){
  salary_new <- salary*1.10
  cat("The new salary is: ", salary)
} else {
  salary <- salary*1.15
  cat("The new salary is: ", salary)
}

```



# 7. Divisible by 3 and 5

```{r}
my.vec <- c(1000:1)

div.vec <- c()
index <- 1

for (n in my.vec){
  if ( (n %% 3 == 0) & (n %% 5 == 0) & (n %% 7 == 0) ){
    if (n == 525){next}
    div.vec[index] <- n
    index <- index + 1
  }
}

div.vec
```



## 8. Value times index

```{r}

## OH! sample.int?!?! Not sample anymore! =O
x <- sample.int(100, 10)
x
typeof(x)
new.vec <- c()
index <- 1
while (index <= length(x)){
  new.vec[index] <- x[index] * index
  index <- index + 1 
}

new.vec

```